\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-04 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
adding IEEE 14 bus sim results

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
We next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
% \begin{align}
% \rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
% 	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
% \label{rho0synthetic}	
% \end{align}
\begin{multline}
\rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right) \\
	\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{multline}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

Fig. \ref{fig:CompTimeSynthetic} highlights that for computing high dimensional transient joint state PDFs as in here, the proposed variational framework enjoys remarkably fast computational time. Notice that constructing histograms or other conventional density estimators for the joint state PDF by making a grid over the 100 dimensional state space, is computationally prohibitive.

>>>>

\subsection{Synthetic Test System}\label{subsec:NumSimSynthetic}
To highlight the scalability of the proposed method, we next consider a power network with $n=50$ generators, and propagate the transient joint state PDFs supported over the 100 dimensional state space $\mathbb{T}^{50}\times\mathbb{R}^{50}$. We take the initial joint state PDF at $t=0$ as
% \begin{align}
% \rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = &\;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right)\nonumber\\
% 	&\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
% \label{rho0synthetic}	
% \end{align}
\begin{multline}
\rho_{0}\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \;{\rm{Unif}}\left(\left([0,2\pi)\;\text{rad}\right)^{n}\right) \\
	\qquad\times {\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right),
\label{rho0synthetic}	
\end{multline}
and following \cite[Sec. 5]{dorfler2012synchronization}, randomly generate the parameters as in Table \ref{table:ParamUncertaintiesSynthetic}. These parameter ranges are consistent with the same found in \cite{sauerpai1998,andersonBook1977,kundurBook1994}.

@@

Fig. \ref{fig:CompTimeSynthetic} highlights that for computing high dimensional transient joint state PDFs as in here, the proposed variational framework enjoys remarkably fast computational time. Notice that constructing histograms or other conventional density estimators for the joint state PDF by making a grid over the 100 dimensional state space, is computationally prohibitive in a general purpose computer.
